---
title: "Group 7: Visualization of Climate Opinion in U.S. States"
author: "Jun Pu, Jenny Ding, Christy Yang"
date: "2024-05-14"
output: 
  ioslides_presentation:
    widescreen: true
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 1. Question
#### What does climate awareness and opinion look like in different states and over time?

- Is high level of awareness/ concern of climate change related to certain demographic features of a state, e.g. income level, education level, etc.?
- As there’re more extreme climate events, do awareness of climate change increase over time?

#### Why is it important?
- Public opinion about global warming is an important influence on decision making about policies to reduce global warming or prepare for the impacts.
- While researchers find increases in global warming issue importance and perceived harm in different states, policy support increased more in certain states (California and New York) than elsewhere ([Marlon and Wang](https://iopscience.iop.org/article/10.1088/1748-9326/aca702/pdf)).

## 2. Hypothesis

- Higher percentage of residents in coastal states will have direct experience with extreme climate events and global warming, thus more likely to be worried about climate change.

- In states with higher percentage of people with higher education degree, residents are likely to be aware of climate change issues and agree with more policy reforms to tackle climate change issues.

- We would likely observe an increase in climate awareness over the past decade.


## 3. Data

- [Yale Climate Opinion Maps (YCOM), 2010 - 2023](https://climatecommunication.yale.edu/visualizations-data/ycom-us/)

- [American Community Survey (ACS), 2022](https://www.census.gov/programs-surveys/acs)

## 3.1 YCOM, 2010 - 2023
- `YCOM` is collected through a national survey and includes data from 2010-2023 for 16 state-level climate opinions.

- The estimates are derived from a large national survey dataset (n>31,000), along with demographic and geographic population characteristics.

- Survey questions include 4 categories: Beliefs, Risk Perceptions, Policy Support, Behaviors.
  - Example question: Do you think that global warming is happening?
  - Multiple choice answers: Yes / No / Don't Know
  - Data is coded as percentage answering *Yes* in a state.

## 3.2 ACS, 2022
- `ACS` is the most comprehensive dataset that covers a wide range of Demographic and Housing Charactersitics including `medium income`, `education level`, etc.
- `ACS` also includes geometry for each state and we used that for mapping.
- With `tidycensus`, we are able to directly select variables of interest and obtain data frames for a specific year.
- The original ACS data is in counts and we standardized them to percentage.
  - Percentage = (Count / Population by ACS)*100
  
## 3.3 Potential Limitations
- The demographic characteristics from the ACS are from the year 2022, and the climate opinion data is also from 2023.
- Both the climate opinion data and ACS data are aggregated estimations that overlook differences among individual states.

## 4. Visualizations
- What is the Relationship Between State-Level Public Opinions on Climate Change Issues (2022) and Demographic Information (2023)? 
  - Shiny app: Map of ACS Demographics and Climate Opinions
- How Do State-Level Extremes in Public Opinion on Climate Change Issues Vary by Year (2010-2023)?
  - Shiny app: dumbbell plot with input year
- What is the Range of Public Opinion on Climate Change Issues Within Specific States Across Multiple Years (2010-2023)?
  - Shiny app: dumbbell plot with input state


## 4.1 Map of both Demographic Characteristics(2023) & Climate Opinions (2023)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load packages
library(shiny)
library(tidyverse)
library(tidycensus)
library(ggiraph)
library(scales)
library(ggplot2)
library(plotly)
library(tigris)
library(readxl)
options(tigris_use_cache = TRUE)

# ACS
var_22 <- load_variables(2022, "acs1", cache = TRUE)

# population data
pop_22 <- get_acs(
  geography = "state",
  variables = "B01003_001",
  year = 2022,
  survey = "acs1",
  geometry = FALSE,
  resolution = "20m"
) |> rename(population = estimate) |>
  select(NAME, population)

# median income in the state
income_22 <- get_acs(
  geography = "state",
  variables = "B25077_001",
  year = 2022,
  survey = "acs1",
  geometry = TRUE,
  resolution = "20m"
)

income_22_shifted <- income_22 |>
  shift_geometry(position = "outside") |>
  mutate(fill_value = estimate) |>
  mutate(tooltip = paste(NAME, fill_value, sep = ": "))

# people with a bachelor's degree
edu_22 <- get_acs(
  geography = "state",
  variables = "B07009_005",
  year = 2022,
  survey = "acs1",
  geometry = TRUE,
  resolution = "20m"
)

edu_22_merge <- merge(edu_22, pop_22, by = "NAME")
edu_22_merge$percentage <- round((edu_22_merge$estimate / edu_22_merge$population) * 100, 1)

edu_22_shifted <- edu_22_merge |>
  shift_geometry(position = "outside") |>
  mutate(fill_value = percentage) |>
  mutate(tooltip = paste(NAME, ":", fill_value, "% of population has a bachelor's degree"))

# foreign born population
foreign_22 <- get_acs(
  geography = "state",
  variables = "B05002_013",
  year = 2022,
  survey = "acs1",
  geometry = TRUE,
  resolution = "20m"
)

foreign_22_merge <- merge(foreign_22, pop_22, by = "NAME")
foreign_22_merge$percentage <- round((foreign_22_merge$estimate / foreign_22_merge$population) * 100, 1)

foreign_22_shifted <- foreign_22_merge |>
  shift_geometry(position = "outside") |>
  mutate(fill_value = percentage) |>
  mutate(tooltip = paste(NAME, ":", fill_value, "% population are foreign born"))

# at or above 150% poverty level
abovepoverty_22 <- get_acs(
  geography = "state",
  variables = "B07012_004",
  year = 2022,
  survey = "acs1",
  geometry = TRUE,
  resolution = "20m"
)

abovepoverty_22_merge <- merge(abovepoverty_22, pop_22, by = "NAME")
abovepoverty_22_merge$percentage <- round((abovepoverty_22_merge$estimate / abovepoverty_22_merge$population) * 100, 1)

abovepoverty_22_shifted <- abovepoverty_22_merge |>
  shift_geometry(position = "outside") |>
  mutate(fill_value = percentage) |>
  mutate(tooltip = paste(NAME, ":", fill_value, "% population at or above 150% poverty level"))

data_23 <- read_excel("YCOM_2023.xlsx")

# separate State-level data from county-level data
state_23 <- subset(data_23, geotype == "state") |>
  rename(NAME = geoname) |>
  select(NAME, citizens, congress, consensus, discuss, exp, happening, human, worried)

# add a row for Puerto Rico with all climate data set to null
state_23 <- state_23 %>%
  add_row(NAME = "Puerto Rico", citizens = NA, congress = NA, consensus = NA, discuss = NA, exp = NA, happening = NA, human = NA, worried = NA)


# merge ACS data with climate change opinion data
data_merged <- merge(income_22, state_23, by = "NAME")

data_merged_shifted <- data_merged |>
  shift_geometry(position = "outside") |>
  mutate(tooltip_discuss = paste(NAME, ":", discuss, "% population that often discuss climate change")) |>
  mutate(tooltip_citizens = paste(NAME, ":", citizens, "% thinking that citizens should do more")) |>
  mutate(tooltip_congress = paste(NAME, ":", congress, "% thinking that the congress should do more")) |>
  mutate(tooltip_consensus = paste(NAME, ":", consensus, "% who believe that global warming is happening")) |>
  mutate(tooltip_exp = paste(NAME, ":", exp, "% personally experienced global warming")) |>
  mutate(tooltip_happening = paste(NAME, ":", happening, "% thinking global warming is happening")) |>
  mutate(tooltip_human = paste(NAME, ":", human, "% agree that global warming is caused by human activities")) |>
  mutate(tooltip_worried = paste(NAME, ":", worried, "% worried about global warming"))

# UI
ui <- fluidPage(
  titlePanel("State-Level Analysis of Demographics (2022) and Climate Change Opinions (2023)"),
  fluidRow(
    column(6,
           selectInput("variable1", "Select Climate Change Opinion Variable:",
                       choices = list(
                         "Discuss Climate Change" = "discuss",
                         "Citizens Should Do More" = "citizens",
                         "Congress Should Do More" = "congress",
                         "Global Warming Consensus" = "consensus",
                         "Experienced Global Warming" = "exp",
                         "Global Warming Happening" = "happening",
                         "Human-Caused Warming" = "human",
                         "Worried About Warming" = "worried"
                       )),
           girafeOutput("map1", height = "600px")
    ),
    column(6,
           selectInput("variable2", "Select Demographic Variable:", 
                       choices = list("Median Housing Value" = "income",
                                      "Education Level" = "edu",
                                      "Foreign Born Population" = "foreign",
                                      "Above Poverty Level" = "abovepoverty")),
           girafeOutput("map2", height = "600px")
    )
  )
)

# Server
server <- function(input, output) {
  
  reactive_data1 <- reactive({
    data_merged_shifted
  })
  
  reactive_title1 <- reactive({
    switch(input$variable1,
           "discuss" = "Percentage of population that often discuss climate change, 2023",
           "citizens" = "Percentage of population thinking that citizens should do more, 2023",
           "congress" = "Percentage of population thinking that the congress should do more, 2023",
           "consensus" = "Percentage of population who believe that global warming is happening, 2023",
           "exp" = "Percentage of population who believe that personally experienced global warming, 2023",
           "happening" = "Percentage of population who think that global warming is happening, 2023",
           "human" = "Percentage who think that global warming is caused mostly by human activities, 2023",
           "worried" = "Percentage who are somewhat/very worried about global warming, 2023")
  })
  
  output$map1 <- renderGirafe({
    data1 <- reactive_data1()
    var1 <- input$variable1
    map1 <- ggplot(data1, aes_string(fill = var1)) +
      geom_sf_interactive(aes_string(tooltip = paste0("tooltip_", var1), data_id = "NAME"), size = 0.1) +
      scale_fill_viridis_c(option = "plasma") +
      labs(title = reactive_title1(),
           caption = "Data source: 2023 Yale Program on Climate Change Communication",
           fill = "% state population") +
      theme_void() +
      theme(plot.title = element_text(size = 10))
    
    girafe(ggobj = map1) |>
      girafe_options(opts_hover(css = "fill:cyan;"), 
                     opts_zoom(max = 10))
  })
  
  reactive_data2 <- reactive({
    switch(input$variable2,
           "income" = income_22_shifted,
           "edu" = edu_22_shifted,
           "foreign" = foreign_22_shifted,
           "abovepoverty" = abovepoverty_22_shifted)
  })
  
  reactive_title2 <- reactive({
    switch(input$variable2,
           "income" = "Median Housing Value by State, 2022",
           "edu" = "Percentage of Population with Bachelor's Degree by State, 2022",
           "foreign" = "Percentage of Population that are Foreign Born, 2022",
           "abovepoverty" = "Percentage of Population that are Above Poverty Level, 2022")
  })
  
  reactive_fill2 <- reactive({
    if (input$variable2 == "income") {
      scale_fill_viridis_c(option = "plasma", labels = label_dollar())
    } else {
      scale_fill_viridis_c(option = "plasma")
    }
  })
  
  output$map2 <- renderGirafe({
    data2 <- reactive_data2()
    map2 <- ggplot(data2, aes(fill = fill_value)) +
      geom_sf_interactive(aes(tooltip = tooltip, data_id = NAME), size = 0.1) +
      reactive_fill2() +
      labs(title = reactive_title2(),
           caption = "Data source: 2022 1-year ACS, US Census Bureau",
           fill = "ACS estimate") +
      theme_void() +
      theme(plot.title = element_text(size = 10))
    
    girafe(ggobj = map2) |>
      girafe_options(opts_hover(css = "fill:cyan;"), 
                     opts_zoom(max = 10))
  })
}

shinyApp(ui = ui, server = server)

```

## 4.2 Plot time series (select year)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot average % by year

# Load packages
library(readxl)
library(dplyr)
library(ggplot2)
library(plotly)
library(tidyr)
library(reshape2)

# Read Data and pivot to long format
df_ts <- read_excel("YCOM_ts.xlsx")%>%
  select(-c("State code"))

# Pivot the dataset to long format
df_ts_long <- pivot_longer(df_ts, 
                           cols = -c(State, Question), 
                           names_to = "year", 
                           values_to = "value")


library(shiny)
library(dplyr)
library(plotly)

# Assuming df_plot is available in your shiny app

ui <- fluidPage(
  titlePanel("Climate Change Opinion Analysis by Year"),
  
  sidebarLayout(
    sidebarPanel(
      sliderInput("year", "Select Year:", min = 2010, max = 2023, value = 2010)
    ),
    mainPanel(
      tags$div(
        style = "margin: 10px;"
      ),
      plotlyOutput("opinion_plot")
    )
  )
)

server <- function(input, output) {
  
  filtered_data <- reactive({
    df_ts_long %>%
      filter(year == input$year) %>%
      group_by(Question) %>%
      summarise(min= min(value), max = max(value), min_state = State[which.min(value)],max_state = State[which.max(value)], diff = max - min)
  })
  
  output$opinion_plot <- renderPlotly({
    plot_ly(filtered_data(), type = 'scatter', mode = 'markers+lines', hoverinfo = 'text') %>%
      add_segments(
        x = ~min, y = ~Question,
        xend = ~max, yend = ~Question,
        color = I("gray"), showlegend = TRUE
      ) %>%
      add_markers(
        x = ~min, y = ~Question,
        color = I("blue"),
        name = "minimum",
        text = ~paste("State:", min_state, "<br>Value:", min,"<br>Diff:", diff)
      ) %>%
      add_markers(
        x = ~max, y = ~Question, 
        color = I("red"),
        name  = "maximum",
        text = ~paste("State:", max_state, "<br>Value:", max,"<br>Diff:", diff)
      ) %>%
      layout(
        xaxis = list(title = "Proportion of people answering 'yes' (%)"),
        yaxis = list(title="Climate Change Questions")
      )
  })
}

shinyApp(ui = ui, server = server)

```

## 4.3 Plot time series (select state)

```{r prec, echo=FALSE, message=FALSE, warning=FALSE}
library(shiny)
library(dplyr)
library(plotly)
library(readxl)
library(tidyr)

# Read Data and pivot to long format
df_ts <- read_excel("YCOM_ts.xlsx") %>%
  select(-c("State code"))

# Pivot the dataset to long format
df_ts_long <- pivot_longer(df_ts, 
                           cols = -c(State, Question), 
                           names_to = "year", 
                           values_to = "value")

ui <- fluidPage(
  titlePanel("Climate Change Opinion Analysis by State"),
  
  sidebarLayout(
    sidebarPanel(
      selectInput("state", "Select State:", choices = unique(df_ts_long$State))
    ),
    mainPanel(
      tags$div(
        style = "margin: 10px;"
      ),
      plotlyOutput("state_opinion_plot")
    )
  )
)

server <- function(input, output) {
  
  filtered_data <- reactive({
    df_ts_long %>%
      filter(State == input$state) %>%
      group_by(Question) %>%
      summarise(min_value = min(value),
                max_value = max(value),
                min_year = year[which.min(value)],
                max_year = year[which.max(value)],
                diff = max_value - min_value)
  })
  
  output$state_opinion_plot <- renderPlotly({
    plot_ly(filtered_data(), type = 'scatter', mode = 'markers+lines') %>%
      add_segments(
        x = ~min_value, y = ~Question,
        xend = ~max_value, yend = ~Question,
        color = I("gray"), showlegend = TRUE
      ) %>%
      add_markers(
        x = ~min_value, y = ~Question,
        color = I("blue"),
        name = "minimum",
        hoverinfo = "text",
        text = ~paste("Year:", min_year, "<br>Value:", min_value, "<br>Diff:", diff)
      ) %>%
      add_markers(
        x = ~max_value, y = ~Question, 
        color = I("red"),
        name  = "maximum",
        hoverinfo = "text",
        text = ~paste("Year:", max_year, "<br>Value:", max_value, "<br>Diff:", diff)
      ) %>%
      layout(
        xaxis = list(title = "Proportion of people answering 'yes' (%)"),
        yaxis = list(title = "Climate Change Questions")
      )
  })
}

shinyApp(ui = ui, server = server)


```


## Thank you and Q&A
